Notes

### 2022-09-22 chapters/experiments.tex
Some corrections after public defense

Figure~\ref{fig:reg_emcee_real} shows the results for the real data sets. In these data sets there is a substantial difference in performance between some of our methods and the reference algorithms. However, the predict-then-summarize approach (represented as \textit{posterior\_mean}) seems to work quite well, always scoring near the mean RMSE of all the comparison algorithms. Moreover, our two-stage methods seem to outperform the summarize-then-predict methods in these cases, scoring again very close to the mean of the reference methods.

@@

In Figure~\ref{fig:clf_emcee_rkhs} we see the results for the GP regressors in the logistic RKHS case. Our models perform fairly well in this advantageous case, although the two-stage methods fare somewhat poorly in these data sets. However, in most cases the differences observed account for only one or two misclassified samples.

@@

Continuing with Figure~\ref{fig:clf_emcee_l2}, we see that in the \(L^2\) case the results are again promising, since our models score consistently on or above the mean of the reference models, and in many cases surpassing most of them. The predict-then-summarize approaches (\textit{emcee\_posterior\_mean} and \textit{emcee\_posterior\_vote}) are particularly good in this case, and in general have low standard errors. Moreover, the overall accuracy of all methods is low (below 60\%), so this is indeed a difficult problem in which even small increases in accuracy are relevant.

@@

As for the real data sets, in Figure~\ref{fig:clf_emcee_real} we see positive results in general, obtaining in most cases accuracies well above the mean of the reference models, and sometimes above most of them. In particular, the predict-then-summarize methods tend to have a good performance and achieve a lower standard error across executions, which is a trend that we also saw in the simulated data sets. However, our variable selection methods seem to be a bit worse in this case. Again, the models that use \textit{emcee\_mean} are the exception, and in all these data sets they perform steadily worse than the rest of our Bayesian models.

>>>>

Figure~\ref{fig:reg_emcee_real} shows the results for the real data sets. In these data sets there is a substantial difference in performance between some of our methods and the reference algorithms. However, the predict-then-summarize approach (represented as \textit{posterior\_mean}) seems to work quite well, always scoring near the mean RMSE of all the comparison algorithms. Moreover, our two-stage methods seem to outperform the summarize-then-predict methods in Moisture and Sugar, scoring again very close to the mean of the reference models.

@@

In Figure~\ref{fig:clf_emcee_rkhs} we see the results for the GP regressors in the logistic RKHS case. Our models perform fairly well in this advantageous case, although they are not always better than the comparison methods. However, in most cases the differences observed account for only one or two misclassified samples.

@@

Continuing with Figure~\ref{fig:clf_emcee_l2}, we see that in the \(L^2\) case the results are again promising, since our models score consistently on or above the mean of the reference models, and in many cases surpassing most of them. The predict-then-summarize approaches (\textit{emcee\_posterior\_mean} and \textit{emcee\_posterior\_vote}) are particularly good in this case, and in general have low standard errors. Moreover, the overall accuracy of all methods is poor (below 60\%), so this is indeed a difficult problem in which even small increases in accuracy are relevant.

@@

As for the real data sets, in Figure~\ref{fig:clf_emcee_real} we see positive results in general, obtaining in most cases accuracies well above the mean of the reference models, and sometimes above most of them. In particular, the predict-then-summarize methods tend to have a good performance and achieve a lower standard error across executions, which is a trend that we also saw in the simulated data sets. As we have been seeing almost invariably, the models that use \textit{emcee\_mean} are the exception, and in all these data sets they perform steadily worse than the rest of our Bayesian models.
